\documentclass[12pt]{article}

\usepackage{booktabs}
\usepackage{dcolumn} 
\usepackage{epstopdf}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{longtable} 
\usepackage{natbib}
\usepackage{rotating}
\usepackage{tabularx}
\usepackage{amsmath}
\usepackage{setspace}
\usepackage{caption}

%\usepackage[utf8]{inputenc}
%\usepackage[russian]{babel}


%\usepackage{fontawesome}
\usepackage[super]{nth}  
\hypersetup{
  colorlinks = TRUE,
  citecolor=blue,
  linkcolor=red,
  urlcolor=black
}

\hypersetup{colorlinks = TRUE, citecolor=blue, linkcolor=red, urlcolor=black}

\DeclareMathOperator*{\argmax}{arg\,max}

\newcommand{\starlanguage}{Significance indicators: $p \le 0.05:*$, $p \le 0.01:**$ and $p \le .001:***$.}

\newcommand{\covid}{Covid-19}  

\newtheorem{proposition}{Proposition}
\newtheorem{assumption}{Assumption}
\newtheorem{example}{Example}
\newtheorem{observation}{Observation}
\newtheorem{lemma}{Lemma}

\newcommand{\important}[1]{\textcolor{blue}{\textbf{ #1}}}
\newcommand{\quantclaim}[1]{\textcolor{red}{\textbf{ #1}}}

\begin{document} 

\title{Covid19 and Work-from-Home:\\ An Early Look}

\date{\today}

\author{Erik Brynjolfsson\\Stanford \& NBER \and John Horton\\MIT \& NBER \and Daniel Rock\\MIT \and Garima Sharma\\University of New Mexico \and Hong Yi To Ye\\MIT}

\maketitle

\begin{abstract}
  \noindent The on-going \covid{} pandemic has confined large numbers of people to their homes and caused unprecedented lay-offs.
  As a response, individuals might attempt to fine ways to work from home.
  In this note, we document a substantial rise in worker sign-ups on Upwork, an online labor market.
  The effects are concentrated in countries reportedly most adverseley affected, with timing consistent the country-specific seriousness of the pandemic.
  We also document several outlier countries that show large growthn than expected. 
%  The timing of singups is consistent with 
  \newline 
%% \noindent JEL J01, J24, J3 \newline 
%% keywords: bargaining, match formation, wage determination
\end{abstract} 

\onehalfspacing 

\section{Introduction}
The on-going \covid{} pandemic has confined large numbers of people to their homes via quarntines and shelter-in-place orders.
Many businesses are closed. 
There have already been enormous and unprecendented increases in workers filing unemployment insurance claims \citep{goldsmith2020}. 
At least some workers have already been laid-off, creating the need to find alternative source of income.
Even workers who are not laid-off now have greater time available. 
Workers seeking more work face a challeng, however, because the pandemic, outside-the-home work opportunities are less attractive or less available.
As such, we might expect an increase in interest in remote work opportunities. 

In this note, we document how \covid{} is affecting signups on Upwork, a large online labor market \cite{horton2010online}.
Our goal is to simply document this margin of adjustment by country.
The fraction of jobs that can potentially be done remotely is lareg \cite{dingel2020}.



\newpage \clearpage
\bibliographystyle{aer}
\bibliography{remote_work.bib}

\end{document} 
